## Jobs & Deposits {.unlisted .unnumbered}

-   Which categories of jobs have the highest and lowest average deposits?

------------------------------------------------------------------------

```{r child='./analytics/a_jobsDeposits.Rmd'}

```

## Jobs & Education Level {.unlisted .unnumbered}

-   What is the dominant educational level of each category of job?

------------------------------------------------------------------------

```{r child='./analytics/b_jobsEducation.Rmd'}

```

## Mortgage & Personal Loans {.unlisted .unnumbered}

-   What percentage of persons have both mortgage and personal loan?

------------------------------------------------------------------------

```{r child='./analytics/c_mortgageLoans.Rmd'}

```

## Age & Highest Balance {.unlisted .unnumbered}

-   Which age-group has the highest average balance?

------------------------------------------------------------------------

```{r child='./analytics/d_ageBalance.Rmd'}

```

## Married & Overdraft {.unlisted .unnumbered}

-   What percentage of customers who are married also are in overdraft?

------------------------------------------------------------------------

```{r child='./analytics/e_marriedOverdraft.Rmd'}

```

## Deposit & Balance {.unlisted .unnumbered}

-   Is there a correlation between deposit and balance? Discuss the findings. Explain the implications.

------------------------------------------------------------------------

```{r child='./analytics/f_depositBalance.Rmd'}

```

## Deposit {.unlisted .unnumbered}

-   Time series graphs to show comparison between deposits made over 2 comparative periods within the data

------------------------------------------------------------------------

```{r child='./analytics/g_depositTime.Rmd'}

```
