## RefNum {.unlisted .unnumbered}

```{r child='./columns/RefNum.Rmd'}

```

## Deposit {.unlisted .unnumbered}

```{r child='./columns/Deposit.Rmd'}

```

## Balance {.unlisted .unnumbered}

```{r child='./columns/Balance.Rmd'}

```

## Job {.unlisted .unnumbered}

```{r child='./columns/Job.Rmd'}

```

## Age {.unlisted .unnumbered}

```{r child='./columns/Age.Rmd'}

```

## Marital {.unlisted .unnumbered}

```{r child='./columns/Marital.Rmd'}

```

## Education {.unlisted .unnumbered}

```{r child='./columns/Education.Rmd'}

```

## Housing {.unlisted .unnumbered}

```{r child='./columns/Housing.Rmd'}

```

## Loan {.unlisted .unnumbered}

```{r child='./columns/Loan.Rmd'}

```

## Contact {.unlisted .unnumbered}

```{r child='./columns/Contact.Rmd'}

```

## Day {.unlisted .unnumbered}

```{r child='./columns/Day.Rmd'}

```

## Month {.unlisted .unnumbered}

```{r child='./columns/Month.Rmd'}

```

## Duration {.unlisted .unnumbered}

```{r child='./columns/Duration.Rmd'}

```

## Last Deposit

```{r child='./columns/LastDeposit.Rmd'}

```
